Mysis analysis

### 2015-10-12 _drafts/mysisAnalysis.Rmd
updated gh pages

```{r loadLibraries, echo=TRUE, include=FALSE, message=FALSE}
options(digits=3)
set.seed(123)
require(knitr)
require(ggplot2)
require(Gmisc)
require(MASS)
require(stringr)
require(mgcv)
require(lme4)

@@

## Model for proportion of juveniles
```{r, echo=TRUE, include=FALSE, message=FALSE, cache=TRUE}
set.seed(123)
data_one_way <- read.csv("~/mysis/data/ttestData.csv", skip = 3, nrows = 40,
                         header = TRUE, stringsAsFactors=FALSE)

prop <- c(as.numeric(data_one_way$full.2),    ## proportion of females full net
             as.numeric(data_one_way$half.2)) ## proportion of females half net
N <- length(prop)
## Set improper values to NA

date <- rep(as.factor(data_one_way$month), 2)
net <- as.factor(c(rep("full", 40), rep("half", 40)))
data <- data.frame(prop=prop, date=date, net=net)
levels(data$date) <- c("July", "August", "Septempber")
levels(data$net) <- c("Small Net", "Large Net")
X <- model.matrix(~ net * date)
library(betareg)
brmod <- betareg(prop ~ . -1, data = data.frame(prop, X))
summary(brmod)
```

>>>>

```{r loadLibraries, echo=TRUE, include=FALSE, message=FALSE}
options(digits=3)
set.seed(123)
require(knitr)
knitr::opts_chunk$set(fig.path='../images/mysisAnalysis-')
require(ggplot2)
require(Gmisc)
require(MASS)
require(stringr)
require(mgcv)
require(lme4)

@@

## Model for proportion of juveniles
```{r, echo=TRUE, include=FALSE, message=FALSE, cache=TRUE}
load("~/mysis/data/mysisSexCountData.RData")
X <- model.matrix(~ net * date)
library(betareg)
brmod <- betareg(prop ~ . -1, data = data.frame(prop, X))
summary(brmod)
```
